### 2021-04-17 paper/calibration_and_estimation.tex
Mention Troeger's research.
Address some LaTeX warnings. Add force option to latex command.
Update Readme and add pdf.

As mentioned in section \ref{sec:matching}, the probability that two individuals are
matched can depend on background characteristics. In particular, we allow this
probability to depend on age and county of residence. While we do not have good data on
geographical assortativeness and just roughly calibrate it such that 60 \% of contacts
are within the same county, we can calibrate the age assortativeness from
the same data we use to calibrate the number of contacts.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9 \textwidth]{../figures/assortative_matching_probability_example.png}
    \caption{Distribution of random non-work contacts by age of participants.}
    \label{fig:assortativeness}
    \figurenotes{
        The figure shows the distribution of random non-work contacts by age groups. A
        row shows the share of contacts a certain age group has with all other age
        groups. Higher values are colored in darker red tones. The diagonal represents
        the share of contacts with individuals from the same age group.
    }
\end{figure}

Figure~\ref{fig:assortativeness} shows that assortativeness by age is especially strong
for children and younger adults. For older people, the pattern becomes more dispersed
around their own age group, but within-age-group contacts are still the most common
contacts.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9 \textwidth]{../figures/work_multiplier.png}
    \caption{Share of workers attending work normally.}
    \label{fig:work_multiplier}
    \figurenotes{
        The figure shows the percentage of pre-pandemic work mobility taking place
        since the start of the pandemic. In our model this is used as a proxy for the
        share of workers that attend work as usual. Workers are ordered with the
        importance of personal contacts for their work. Thus, if the share of
    }
\end{figure}

>>>>

As mentioned in section \ref{sec:matching}, the probability that two individuals are
matched can depend on background characteristics. In particular, we allow this
probability to depend on age and county of residence. While we do not have good data on
geographical assortativity and just roughly calibrate it such that 60 \% of contacts are
within the same county, we can calibrate the assortative mixing by age from the same
data we use to calibrate the number of contacts.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.9 \textwidth]{../figures/assortative_matching_probability_example.png}
    \caption{Distribution of random non-work contacts by age of participants.}
    \label{fig:assortativity}
    \figurenotes{
        The figure shows the distribution of random non-work contacts by age groups. A
        row shows the share of contacts a certain age group has with all other age
        groups. Higher values are colored in darker red tones. The diagonal represents
        the share of contacts with individuals from the same age group.
    }
\end{figure}

Figure~\ref{fig:assortativity} shows that assortativity by age is especially strong
for children and younger adults. For older people, the pattern becomes more dispersed
around their own age group, but within-age-group contacts are still the most common
contacts.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=1.1 \textwidth]{../figures/work_multiplier.png}
    \caption{Share of workers attending work normally.}
    \label{fig:work_multiplier}
    \figurenotes{
        The figure shows the percentage of pre-pandemic work mobility taking place
        since the start of the pandemic. In our model this is used as a proxy for the
        share of workers that attend work as usual. Workers are ordered with the
        importance of personal contacts for their work. Thus, if the share of
    }
\end{figure}

### 2021-04-17 paper/model/initial_conditions.tex
Update Readme and add pdf.

Consider a situation where you want to start a simulation with the beginning set amidst
the pandemic. It means that several thousands of individuals should already have
recovered from the disease, be infectious, symptomatic or in intensive care at the start
of your simulation.
Additionally, the sample of infectious people who will determine the course of the
pandemic in the following periods is likely not representative of the whole population
because of differences in behavior (number of contacts, assortativeness), past policies
(school closures), etc..
The distribution of courses of diseases in the population at the begin of the simulation is
called initial conditions.

>>>>

Consider a situation where you want to start a simulation with the beginning set amidst
the pandemic. It means that several thousands of individuals should already have
recovered from the disease, be infectious, symptomatic or in intensive care at the start
of your simulation. Additionally, the sample of infectious people who will determine the
course of the pandemic in the following periods is likely not representative of the
whole population because of differences in behavior (number of contacts,
assortativity), past policies (school closures), etc.. The distribution of courses of
diseases in the population at the begin of the simulation is called initial conditions.
